Probe or Wait: Handling tail losses using Multipath TCP

### 2017-04-27 main.tex
Template update
added copyright info
tweaked ack-text
fixed figure placement

\documentclass[10pt,conference,compsoc]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[nocompress]{cite}
\usepackage{caption}
\usepackage{subcaption}

@@

\author{\IEEEauthorblockN{Kiran~Yedugundla, Per~Hurtig, Anna~Brunstrom}
\IEEEauthorblockA{Dept. of Computer Science, Karlstad University, Karlstad, Sweden}}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth]{images/fortest.pdf}
\caption{Topology used for Emulation}\label{fig1}
\end{center}
\end{figure}
%\kern-1em
\section{Experimental Setup}\label{exsetup}

@@

\begin{center}

\begin{table}
\resizebox{0.45\textwidth}{!}{\begin{minipage}{0.45\textwidth}
\small
\begin{center}
\begin{tabular}{|c|cccccccccc|}
      \hline

@@

@@

\kern-1em
\section{Observations and Discussion}\label{disc}
This section provides the performance analysis of TCP and MPTCP for the considered cases of single packet tail loss, two packet tail loss and retransmission or probe loss.
\kern-5em
\begin{figure*}[!tbp]
 \begin{subfigure}[b]{0.32\textwidth}
	\includegraphics[angle=0, width=\textwidth,natwidth=578.16,natheight=433.62]{plots/T1P.pdf}
	\caption{Single packet}\label{t1p}
 \end{subfigure}
 \hfill
 \begin{subfigure}[b]{0.32\textwidth}
	\includegraphics[angle=0, width=\textwidth,natwidth=578.16,natheight=433.62]{plots/T2P.pdf}
	\caption{Two packets }\label{t2p}
 \end{subfigure}
 \hfill
 \begin{subfigure}[b]{0.32\textwidth}
	\includegraphics[angle=0, width=\textwidth, natwidth=578.16,natheight=433.62]{plots/T1PP.pdf}
	\caption{Single packet and probe loss }\label{t1pp}
 \end{subfigure}
 \caption{Tail loss scenarios using TCP}\label{tcpf}
\end{figure*}
\subsection{TCP}
Retransmission behavior of TCP provides a base case for MPTCP performance as each individual MPTCP subflow is a TCP flow in itself. Our analysis
starts with the results using TCP and compare it with that of MPTCP. Figure~\ref{tcpf} represent the comparison of TCP 
burst completion times. Path asymmetry is irrelevant in this case as TCP uses a single path.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth]{images/timingER3NewTLP1.pdf}
\end{center}
\caption{Timing diagram of MPTCP behavior with proposed improvements with loss of a) Single packet b) Two packets c) Single packet and probe loss}\label{timingNew}
\end{figure}

@@

\begin{figure*}[!tbp]
\begin{subfigure}[b]{0.32\textwidth}
\includegraphics[angle=0, width=\textwidth, natwidth=578.16,natheight=433.62]{plots/1PNew.pdf}
\caption{Single packet}\label{1pn}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.32\textwidth}
\includegraphics[angle=0, width=\textwidth, natwidth=578.16,natheight=433.62]{plots/2PNew.pdf}
\caption{Two packets}\label{2pn}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.32\textwidth}
\includegraphics[angle=0, width=\textwidth, natwidth=578.16,natheight=433.62]{plots/1PPNew.pdf}
\caption{Single packet and probe loss}\label{1ppn}
\end{subfigure}
\caption{Performance comparison of MPTCP-New with MPTCP and TCP}\label{mpnew}
\end{figure*}

@@

>>>>

\documentclass[10pt,conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[nocompress]{cite}
\usepackage{caption}
\usepackage{subcaption}

@@

\author{\IEEEauthorblockN{Kiran~Yedugundla, Per~Hurtig, Anna~Brunstrom}
\IEEEauthorblockA{Dept. of Computer Science, Karlstad University, Karlstad, Sweden\\
    \{name.surname\}@kau.se
}}

\IEEEoverridecommandlockouts
\IEEEpubid{%
   \makebox[\columnwidth]{ISBN 978-3-901882-94-4~\copyright~2017 IFIP \hfill}%
   \hspace{\columnsep}%
   \makebox[\columnwidth]{ }%
}

@@

%\kern-1em
\section{Experimental Setup}\label{exsetup}
\begin{figure}
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth]{images/fortest.pdf}
\caption{Topology used for Emulation}\label{fig1}
\end{center}
\end{figure}

@@

\begin{center}
    \begin{table}
\resizebox{0.45\textwidth}{!}{\begin{minipage}{0.45\textwidth}
\small
\begin{center}
\begin{tabular}{|c|cccccccccc|}
      \hline

@@

\begin{figure*}
 \begin{subfigure}{0.32\textwidth}
	\includegraphics[angle=0, width=\textwidth,natwidth=578.16,natheight=433.62]{plots/T1P.pdf}
	\caption{Single packet}\label{t1p}
 \end{subfigure}
 \hfill
 \begin{subfigure}{0.32\textwidth}
	\includegraphics[angle=0, width=\textwidth,natwidth=578.16,natheight=433.62]{plots/T2P.pdf}
	\caption{Two packets }\label{t2p}
 \end{subfigure}
 \hfill
 \begin{subfigure}{0.32\textwidth}
	\includegraphics[angle=0, width=\textwidth, natwidth=578.16,natheight=433.62]{plots/T1PP.pdf}
	\caption{Single packet and probe loss }\label{t1pp}
 \end{subfigure}
 \caption{Tail loss scenarios using TCP}\label{tcpf}
\end{figure*}

@@

\section{Observations and Discussion}\label{disc}
This section provides the performance analysis of TCP and MPTCP for the considered cases of single packet tail loss, two packet tail loss and retransmission or probe loss.
\subsection{TCP}
Retransmission behavior of TCP provides a base case for MPTCP performance as each individual MPTCP subflow is a TCP flow in itself. Our analysis
starts with the results using TCP and compare it with that of MPTCP. Figure~\ref{tcpf} represent the comparison of TCP 
burst completion times. Path asymmetry is irrelevant in this case as TCP uses a single path.

@@

\begin{figure*}
\begin{subfigure}[b]{0.32\textwidth}
\includegraphics[angle=0, width=\textwidth, natwidth=578.16,natheight=433.62]{plots/1PNew.pdf}
\caption{Single packet}\label{1pn}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.32\textwidth}
\includegraphics[angle=0, width=\textwidth, natwidth=578.16,natheight=433.62]{plots/2PNew.pdf}
\caption{Two packets}\label{2pn}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.32\textwidth}
\includegraphics[angle=0, width=\textwidth, natwidth=578.16,natheight=433.62]{plots/1PPNew.pdf}
\caption{Single packet and probe loss}\label{1ppn}
\end{subfigure}
\caption{Performance comparison of MPTCP-New with MPTCP and TCP}\label{mpnew}
\end{figure*}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth]{images/timingER3.pdf}
\end{center}
\caption{Timing diagram of MPTCP behavior with proposed improvements with loss of a) Single packet b) Two packets c) Single packet and probe loss}\label{timingNew}
\end{figure}

@@

@@

\section*{Acknowledgment}
This work was in part funded by The Knowledge Foundation (KKS) through the SIDUS READY project.
The views expressed are solely those of the author(s).
